Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-03-11 prevalence_testing/postshocktest2021draft.tex
changes of plot and addition for the steps of variable selection

>>>>

The variable selection steps are outlined as follows. At first, we have the same set of covariates $\{\mc{X}_1, \ldots, \mc{X}_p\}$ for each donor, where $\mc{X}_1$ corresponds to the name of the covariate. Next, for each donor, we conduct stepwise variable selection based on AIC so that for each donor, we end up with a model with covariates that may differ across  donors, say $\{\mc{X}_j \colon j\in \mc{I}_i\}$ for $i = 2, \ldots, n+1$, where $\mc{I}_j$ is the collection of the indices corresponding to which covariate is selected. Next, we  take the union $\cup_{i=2}^{n+1}\{\mc{X}_j \colon j\in \mc{I}_i\}$ to obtain the final set of covariates that are present in the model of every donor and the time series of interest.
